Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
INITIAL SUBMISSION

\cref{fig:rl} shows training curves for using \our as the dynamic model (\lab{color-our}), along with a Laplace-GGN~\cite{todo} with GLM predictions (\lab{red}), an ensemble of neural networks (\lab{color-ensemble}), and a basic MLP without uncertainty (\lab{color-mlp}). To ensure a fair comparison, we maintain the same MLP architecture/training scheme across all these methods and incorporate them into the same model-based RL algorithm (see \cref{app:rl}). We also compare our results with Deep Deterministic Policy Gradient (DDPG, \cite{lillicrapContinuousControlDeep2016}), a model-free RL algorithm (\lab{color-ddpg}).
%
The training curves clearly show that \our's uncertainty estimates help exploration as it converges in fewer episodes, demonstrating higher sample efficiency. As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.

@@

 \end{tikzpicture}}\\[2em]~
 \end{subfigure}
 \hfill
 \begin{subfigure}[c]{.7\textwidth}
   \raggedleft\scriptsize
   \setlength{\figurewidth}{\textwidth}
   \setlength{\figureheight}{.55\figurewidth}
   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(-.1,-.1)},anchor=south east}}
   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,densely dotted}}
   \hspace*{-1.7cm}%
   \def\our{{\sc sfr} (ours)}
   \input{./fig/rl.tex}
 \end{subfigure}\\[-1.5em]
 \caption{\textbf{Cartpole swingup with sparse reward.} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.
   Our method (\lab{color-our}) converges in fewer environment steps than the baseline model-based RL method and DDPG, the model-free baseline. The dashed lines mark the asymptotic return for the methods not coverged in the plot.}
 \label{fig:rl}
\end{figure}

>>>>

\cref{fig:rl} shows training curves for using \our as the dynamic model (\lab{color-our}), along with a Laplace-GGN~\cite{immer2021scalable} with GLM predictions (\lab{red}), an ensemble of neural networks (\lab{color-ensemble}), and a basic MLP without uncertainty (\lab{color-mlp}). To ensure a fair comparison, we maintain the same MLP architecture/training scheme across all these methods and incorporate them into the same model-based RL algorithm (see \cref{app:rl}). We also compare our results with Deep Deterministic Policy Gradient (DDPG, \cite{lillicrapContinuousControlDeep2016}), a model-free RL algorithm (\lab{color-ddpg}).
The training curves show that \our's uncertainty estimates help exploration as it converges in fewer episodes, demonstrating higher sample efficiency.
As expected, the MLP strategy (without uncertainty) was not able to successfuly explore the environment.\looseness-2

@@

 \end{tikzpicture}}\\[2em]~
 \end{subfigure}
 \hfill
 \begin{subfigure}[c]{.7\textwidth}
   \raggedleft\scriptsize
   \setlength{\figurewidth}{\textwidth}
   \setlength{\figureheight}{.55\figurewidth}
   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none},legend style={at={(-.1,-.1)},anchor=south east}}
   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,densely dotted}}
   \hspace*{-1.7cm}%
   \def\our{{\sc sfr} (ours)}
   \input{./fig/rl.tex}
 \end{subfigure}\\[-1.5em]
 \caption{\textbf{Cartpole swingup with sparse reward.} Training curves showing that \our's uncertainty estimates improve sample efficiency in RL.
   Our method (\lab{color-our}) converges in fewer environment steps than the baseline model-based RL method and DDPG, the model-free baseline. The dashed lines mark the asymptotic return for the methods not coverged in the plot.}
 \label{fig:rl}
 \vspace*{-1em}
\end{figure}
